---
title: "Porites astreoides Survival Analysis"
author: "Rachel Ionata"
date: "2023-11-30"
output: html_document
---
# Analyzing Porites astreoides Survival Data (Using Porites Survival by Tile excel sheet)

## Adding Libraries and attaching csv
```{r echo=FALSE, warning=FALSE} 

library(pgirmess) 

library(asbio)

library(tidyverse)

PAST_Survial<-read_csv("Porites Survival by Tile csv.csv")

```

# Trying one way ANOVA with %survival by tile. (Using Porites Survival by Tile excel sheet)
## p-value <.05 need to be transformed
```{r}
PAST_Survial<- PAST_Survial %>% 
  mutate(Group=factor(Group))

p <- ggplot(PAST_Survial, aes(x=Group, y=Prop_Survival)) + 
  geom_boxplot()
p
#Groups 1 and 2 look ok, 3 nd 4 not so much?

shapiro.test (subset(PAST_Survial, Group=='1')$Prop_Survival)


```


# Transformation by square root
```{r}
PAST_Survial_sqrt <- PAST_Survial %>% 
  mutate(Prop_Survival=sqrt(Prop_Survival))


p2 <- ggplot(PAST_Survial_sqrt, aes(x=Group, y=Prop_Survival)) + 
  geom_boxplot()
p2

shapiro.test (subset(PAST_Survial_sqrt, Group=='1')$Prop_Survival)
  

```


## Non-parametric test: Kruskal-Wallis test
```{r}
PAST_Survial %>% 
  kruskal.test(Prop_Survival~Group, data=.)

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
